Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

insert_minor <- function(major, n) {
  minor <- major
  minor[-seq(1, length(major), n)] <- ""
  minor
}

@@

  brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       	       shape = gatherings,
		       color = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  #   scale_color_stata() +
  #   scale_fill_stata() +
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 	 
         guides(
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          color = guide_legend(keywidth = 5, title = "Gatherings"),		  
       	          fill = "none" # guide_legend(title = "Gatherings"),
       	          #color = "none" # guide_legend(title = "Gatherings")
		  )

@@

pics <- list()
brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = "black") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +        
       ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
       xlab("Publication year") +
       ylab("Title length (word count)")
}

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 20)

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Publication year") +
     scale_fill_stata() 
     if (varname == "n") {
       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count frequency (%)") 
     }
     if (varname == "paper") {
       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = "")) 
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5))

@@

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +               
       ggtitle(catal)

@@

theme_set(theme_bw(20))
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(catal)

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
     xlab("Publication year") +
     ylab("Title count (n)")

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
      xlab("Year") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)"))
print(p)
```

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count per capita (n)") +
       scale_color_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +             
       ggtitle("Title count per capita") +
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +   
       ggtitle("Octavo: paper consumption") +
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df$publication_place[!df$publication_place == "Stockholm"] <- "Other"
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(color = "black", aes(fill = publication_place),
         position = "dodge", stat = "identity") +
       xlab("Publication year") +
       ylab("Title length (words)") +
       ggtitle("Mean title length") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
       #scale_fill_manual(values = c("darkgray", "lightgray")) +       
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +         
       ylab("Title count (n)") +
       xlab("Publication year")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) + 
       scale_color_stata() +
       ggtitle(catalogue)       
  print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language)) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +        
       ggtitle(catalogue)

>>>>

insert_minor <- function(major, n, start = NULL) {
  minor <- major
  ind <- ifelse (!is.null(start), which.min(abs(major - start)), 1)
  minor[-seq(ind, length(major), n)] <- ""
  minor
}

@@

  #brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)
  brs <- seq(min(df2$publication_decade), max(df2$publication_decade), 10)

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       	       shape = gatherings,
		       linetype = gatherings
		       ))
  p <- p + geom_point(size = 4)

  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))  
  #   scale_color_stata() +
  #   scale_fill_stata() +
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))

  p <- p + guides(
    color = guide_legend(keywidth = 5, title = "Gatherings"),
    fill = guide_legend(keywidth = 5, title = "Gatherings"),     
    shape = guide_legend(keywidth = 5, title = "Gatherings", reverse = TRUE),
    linetype = guide_legend(keywidth = 5, title = "Gatherings", reverse = TRUE))

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(df2$publication_decade) + 50))

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = "black") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +   
       ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
       xlab("Publication year") +
       ylab("Title length (words)")
}

@@

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Publication year") +
     scale_fill_stata() 
     if (varname == "n") {
       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count frequency (%)") 
     }
     if (varname == "paper") {
       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = "")) 
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))

@@

df$period <- format_period(df$period)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +   
       ggtitle(catal)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Publication year") +
       ylab("Unique publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(catal)

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 1)) +
     xlab("Publication year") +
     ylab("Title count (n)")

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Year") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)"))
print(p)
```

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count per capita (n)") +
       scale_color_stata() +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +                    
       ggtitle("Title count per capita") +
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +                           
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +   
       ggtitle("Octavo: paper consumption") +
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df$publication_place[!df$publication_place == "Stockholm"] <- "Other"
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(color = "black", aes(fill = publication_place),
         position = "dodge", stat = "identity") +
       xlab("Publication year") +
       ylab("Title length (words)") +
       ggtitle("Mean title length") +
       scale_fill_stata() +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +          
       #scale_fill_manual(values = c("darkgray", "lightgray")) +       
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +                 
       ylab("Title count (n)") +
       xlab("Publication year")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +       
       scale_color_stata() +
       ggtitle(catalogue)       
  print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language)) +       
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +      
       ggtitle(catalogue)
